\newglossaryentry{vector}{name=Vectors, text=vector, description={Multidimensional quantities which have both a magnitude (3 meters, 10 km/hour) and a direction (45 degrees, south-southwest)}}
\newglossaryentry{mass}{name=Mass, text=mass, description={A measurement how much matter is in an object.  Mass is independent of gravity: a 3kg rock on earth is still 3kg on the moon, because the amount of matter in the rock doesn't change}}
\newglossaryentry{torque}{name=Torque, text=torque, description={A measurement of twisting force, measured in Newton-meters}} \newglossaryentry{force}{name=Force, text=force, description={A description of the amount of push on an object, and is measured in Newtons.  Force causes a change in motion, described by the equation $\mathbf{F}=m\cdot \mathbf{a}$}}
\newglossaryentry{geardown}{name={Gearing down}, text={gearing down}, description={Using a small gear, sprocket, or pulley to drive a larger gear, sprocket, or pulley, resulting in lower speed but higher torque}}
\newglossaryentry{gearup}{name={Gearing up}, text={gearing up}, description={Using a large gear, sprocket, or pulley to drive a smaller gear, sprocket, or pulley, resulting in higher speed but lower torque}}
\newglossaryentry{rpm}{name=RPM, description={Revolutions Per Minute, a measurement of rotational speed. 1 revolution is one 360-degree turn of a shaft}}
\newglossaryentry{stalled}{name=Stall, text=stalled, description={When a motor can't produce enough torque to turn and stops moving.  This is generally undesireable, and can cause some motors to burn out}}
\newglossaryentry{friction}{name=Friction, text=friction, description={a force that opposes motion, caused by TODO surfaces}}
\newglossaryentry{charge}{name={Electrical charge}, text=charge, description={is TODO}}
\newglossaryentry{current}{name={Electrical current}, text=current, description={is the flow of electrons through a wire, measured in Amps}}
\newglossaryentry{energy}{name=Energy, text=energy, description={is TODO}}
\newglossaryentry{amp}{name=Amp, text=amp, description={The unit for electrical current.  1 Amp is equivalent to 1 Coloumb per second}}
\newglossaryentry{weight}{name=Weight, text=weight, description={is the force due to an object's mass and gravity. Because weight is dependant on gravity, a 3kg rock would weigh more on Earth than on the moon}}
\newglossaryentry{loss}{name=Loss, text=loss, description={is TODO}}
\newglossaryentry{sigfig}{name={Significant figure}, text={significant figure}, description={is TODO}}
\newglossaryentry{joule}{name=Joule, description={One of the SI units for energy}}
\newglossaryentry{efficiency}{name=Efficiency, text=efficiency, description={The ratio of input power to output power.  If a motor puts out 5 units of useful energy for every 10 units put into it, it has an efficiency of 50\%}}
\newglossaryentry{power}{name=Power, text=power, description={The rate at which energy is being used.  Power is typically measured in Watts}}
\newglossaryentry{watt}{name=Watt, text=watt, description={The unit for energy, equivalent to 1 Joule per second}}
\newglossaryentry{normalforce}{name={Normal force}, text={normal force}, description={is the force perpendicular (normal) to a surface. If you are standing on a level floor, the force of your body on the floor is perpendicular to the floor.}}

